Motor Traffic Collision Patterns in Toronto: Analysis based on Environmental Conditions and Driver Behaviours

### 2024-12-04 paper/paper.qmd
Refine the title and readme

---
title: "Environmental Conditions and Driver Behavior Affect Collision Outcomes in Toronto"
subtitle: "A Two-Stage Bayesian Analysis Shows Infrastructure Factors Predict Crash Occurrence While Driver Actions Determine Severity"
author: Yitong Wang
thanks: "Code and data are available at: [https://github.com/demainwang/Toronto_vehicle_collision_analysis](https://github.com/demainwang/Toronto_vehicle_collision_analysis)."
date: today
date-format: long
abstract: "This study employs a two stage bayesian modeling approach to analyze vehicle collision patterns in Toronto, examining how environmental conditions and driver behavior influence both injury occurrence and severity. The first model predicts the probability of injury based on environmental and infrastructural factors, while the second estimates injury severity using driver characteristics and behavior. Analysis of historical collision data from 2006 to 2023 shows that while environmental conditions primarily influence injury occurrence, driver behavior factors like speeding and alcohol use more strongly affect severity levels. These findings demonstrate the need for a dual-pronged approach to urban safety through targeted infrastructure improvements in high-risk areas to prevent collisions, alongside enhanced enforcement strategies focusing on dangerous driving behaviors. "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Motor Traffic Collision Patterns in Toronto: Analysis based on Environmental Conditions and Driver Behaviours"
subtitle: "A Two-Stage Bayesian Analysis Shows Infrastructure Factors Predict Crash Occurrence While Driver Actions Determine Severity"
author: Yitong Wang
thanks: "Code and data are available at: [https://github.com/demainwang/Toronto_vehicle_collision_analysis](https://github.com/demainwang/Toronto_vehicle_collision_analysis)."
date: today
date-format: long
abstract: "This study employs a two stage bayesian modeling approach to analyze vehicle collision patterns in Toronto, examining how environmental conditions and driver behavior influence both injury occurrence and severity. The first model predicts the probability of injury based on environmental and infrastructural factors, while the second estimates injury severity using driver characteristics and behavior. Analysis of historical collision data from 2006 to 2023 shows that while environmental conditions primarily influence injury occurrence, driver behavior factors like speeding and alcohol use more strongly affect severity levels. These findings demonstrate the need for a dual-pronged approach to urban safety through targeted infrastructure improvements in high-risk areas to prevent collisions, alongside enhanced enforcement strategies focusing on dangerous driving behaviors."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
